---
title: "7.2 Assignment"
author: "Anna Harvey"
date: "7/19/2020"
output:  word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fit a logistic regression model to the binary-classifier-data.csv dataset from the previous assignment.

```{r, include=FALSE}
setwd("/users/Anna/Documents/GitHub/dsc520/assignments")
binary <- read.csv("binary-classifier-data.csv")
logregmodel <- glm(label ~ x + y, data = binary)
library(caTools)
```
### a. What is the accuracy of the logistic regression classifier?

```{r}
#Split the data into training and testing sets
split <- sample.split(binary, SplitRatio = 0.8)
train <- subset(binary, split == TRUE)
test <- subset(binary, split == FALSE)

#Create the GLM with the training set
mod <- glm(label ~ x + y, data = binary)

#Run the data through the model
res <- predict(mod, test, type = "response")
res <- predict(mod, train, type = "response")

#Validate model with confusion matrix
confmatrix <- table(Actual_value = train$label, Predicted_value = res > 0.5)
confmatrix

#Calculate accuracy
accresult <- signif((((confmatrix[[1,1]] + confmatrix[[2,2]]) / sum(confmatrix))*100), digits=5)
print(paste("Accuracy = ", accresult, "%"))
```

### b. How does the accuracy of the logistic regression classifier compare to the nearest neighbors algorithm?

```{r}
#Generate random number that is 90% of the total number of rows in dataset
ran <- sample(1:nrow(binary), 0.9 * nrow(binary))

#Normalization function
nor <- function(x) {(x-min(x)/(max(x)-min(x)))}

#Run normalization on the 3 columns of dataset because they are the predictors
binary_norm <- as.data.frame(lapply(binary[,c(1,2,3)], nor))
summary(binary_norm)

#Extract training set
binary_train <- binary_norm[ran,]

#Extract testing set
binary_test <- binary_norm[-ran,]

#Extract 1st column of train dataset because it will be used as 'cl' argument in knn function
binary_target_category <- binary[ran, 1]

#Extract 1st column of test dataset to measure the accuracy
binary_test_category <- binary[-ran, 1]
library(class)

#Run knn function
pr <- knn(binary_train, binary_test, cl=binary_target_category, k = 39)

#Create confusion matrix
tab <- table(pr, binary_test_category)

#Divides correct predictions by total number of predictions to tell us how accurate the model is
accuracy <- function(x) (sum(diag(x))/(sum(rowSums(x)))*100)
print(paste("Accuracy = ", accuracy(tab), "%"))
```

### c. Why is the accuracy of the logistic regression classifier different from that of the nearest neighbors?

The KNN algorithm calculates accuracy by checking the 39 nearest neighbors of the predicted value (k=39) to determine the category. The logistic regression classifier calculates the overall accuracy of the model.
