---
title: "7.2 Assignment"
author: "Anna Harvey"
date: "7/19/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fit a logistic regression model to the binary-classifier-data.csv dataset from the previous assignment.

```{r, include=FALSE}
setwd("/users/Anna/Documents/GitHub/dsc520/assignments")
binary <- read.csv("binary-classifier-data.csv")
logregmodel <- glm(label ~ x + y, data = binary)
```
###a. What is the accuracy of the logistic regression classifier?
```{r}
#Validate model with confusion matrix
confmatrix <- table(Actual_value = binary$label, Predicted_value = res > 0.5)
confmatrix

#Calculate accuracy
accresult <- signif((((confmatrix[[2,2]] + confmatrix[[2,2]]) / sum(confmatrix))*100), digits=5)
accresult
```

###b. How does the accuracy of the logistic regression classifier compare to the nearest neighbors algorithm?

###c. Why is the accuracy of the logistic regression classifier different from that of the nearest neighbors?
