---
title: "8.2 Assignment"
author: "Anna Harvey"
date: "7/25/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## a. Plot the data from each dataset using a scatter plot.
```{r, include=FALSE}
setwd("/users/Anna/Documents/GitHub/dsc520/data")
library(ggplot2)
library(class)
binary <- read.csv("binary-classifier-data.csv")
trinary <- read.csv("trinary-classifier-data.csv")
```
```{r}
ggplot(binary, aes(x = x, y = y)) + geom_point()
ggplot(trinary, aes(x = x, y = y)) + geom_point()
```

## b. Fit a k nearest neighbors model for each dataset for k=3, k=5, k=10, k=15, k=20, and k=25. Compute the accuracy of the resulting models for each value of k. Plot the results in a graph where the x-axis is the different values of k and the y-axis is the accuracy of the model.

```{r, include = FALSE}
knn_accuracy <- function(ds, k) {
    ran <- sample(1:nrow(ds), 0.9 * nrow(ds))
    nor <- function(x) {(x-min(x)/(max(x)-min(x)))}
    norm <- as.data.frame(lapply(ds[,c(1,2,3)], nor))
    train <- norm[ran,]
    test <- norm[-ran,]
    target_category <- ds[ran, 1]
    test_category <- ds[-ran, 1]
    pr <- knn(train, test, cl=target_category, k = k)
    tab <- table(pr, test_category)
    accuracy <- function(x) (sum(diag(x))/(sum(rowSums(x)))*100)
    accuracy(tab)
}
```
```{r, echo = FALSE}
"For binary dataset:"
knn_accuracy(binary, 3)
knn_accuracy(binary, 5)
knn_accuracy(binary, 10)
knn_accuracy(binary, 15)
knn_accuracy(binary, 20)
knn_accuracy(binary, 25)

"For trinary dataset:"
knn_accuracy(trinary, 3)
knn_accuracy(trinary, 5)
knn_accuracy(trinary, 10)
knn_accuracy(trinary, 15)
knn_accuracy(trinary, 20)
knn_accuracy(trinary, 25)
```
```{r, echo = FALSE}
#Create dataframes for graphing
k_vals <- c(3,5,10,15,20,25)
binary_acc <- c(knn_accuracy(binary, 3),
knn_accuracy(binary, 5),
knn_accuracy(binary, 10),
knn_accuracy(binary, 15),
knn_accuracy(binary, 20),
knn_accuracy(binary, 25))

binary_df <- data.frame(k_vals, binary_acc)

trinary_acc <- c(knn_accuracy(trinary, 3),
knn_accuracy(trinary, 5),
knn_accuracy(trinary, 10),
knn_accuracy(trinary, 15),
knn_accuracy(trinary, 20),
knn_accuracy(trinary, 25))

trinary_df <- data.frame(k_vals, trinary_acc)

combo_df <- merge(binary_df, trinary_df)

ggplot(data = combo_df) + geom_point(aes(x = k_vals, y = binary_acc)) + 
    geom_point(aes(x = k_vals, y = trinary_acc)) + 
    labs(title = "Accuracy vs K-values", y ="% Accuracy", x = "K-value") + scale_color_manual(name="Data", 
                        labels = c("Binary", 
                                   "Trinary"), 
                        values = c("Binary"="blue", 
                                   "Trinary"="red" 
                                   ))
    
```


## c. Looking back at the plots of the data, do you think a linear classifier would work well on these datasets?

I do not think that a linear classifier would work well with these datasets because the results are not linear.
